### 2017-03-24 paper/oopsla17-submission/evaluation-accuracy.tex
more eval

\paragraph{Classifiers}
We compare five classifiers, each trained on a full set of 276 features:
44 local syntactic features, 176 contextual syntactic features, 55
typing features, and a single expression size feature.
%
\ES{should explain the make-up of these groups}
%
We preemptively discard expressions that are not part of the minimal
type error slice, we will explain the rationale for this in
\autoref{sec:feature-utility}.
%
Our classifiers are:
%
\begin{enumerate}
\item A logistic regression trained with a learning rate
  $\alpha = 0.001$, an L2 regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item A decision tree \ES{HUMA: hyperparams?}.
\item A random forest with 30 estimators \ES{HUMA: hyperparams?}.
\item Two multi-layer perceptrons, both trained with $\alpha = 0.001$,
  $\lambda = 0.001$, and a mini-batch size of 200. The first MLP
  contains a single hidden layer of 10 neurons, and the second contains
  a hidden layer of 500 neurons. This allows us to investigate how well
  the MLP can \emph{compress} its model.
\end{enumerate}
%
All classifiers were trained for 20 iterations one dataset before being
evaluated on the other.

@@

\autoref{fig:accuracy-results} shows the results of our experiment.

>>>>

Comparing source locations from multiple tools with their own parsers is
not trivial.
%
In order to ensure a fair comparison when evaluating \mycroft and
\sherrloc, we ignored program where they predicted locations that our
oracle could not match with a program expression --- 6--8\% of programs
for \mycroft and 3--4\% for \sherrloc.
%
We also ignored programs where \mycroft or \sherrloc timed out (after
one minute) or where they encountered an unsupported language feature ---
another 5\% for \mycroft and 12--13\% for \sherrloc.

\paragraph{Our Classifiers}
We evaluate five classifiers, each trained on the full set of 276
features: 44 local syntactic features, 176 contextual syntactic
features, 55 typing features, and a single expression size feature.
%
\ES{should explain the make-up of these groups}
%
We preemptively discard expressions that are not part of the minimal
type error slice, we will explain the rationale for this in
\autoref{sec:feature-utility}.
%
Our classifiers are:
%
\begin{enumerate}
\item A logistic regression trained with a learning rate
  $\alpha = 0.001$, an L2 regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item A decision tree \ES{HUMA: hyperparams?}.
\item A random forest with 30 estimators \ES{HUMA: hyperparams?}.
\item Two multi-layer perceptrons, both trained with $\alpha = 0.001$,
  $\lambda = 0.001$, and a mini-batch size of 200. The first MLP
  contains a single hidden layer of 10 neurons, and the second contains
  a hidden layer of 500 neurons. This allows us to investigate how well
  the MLP can \emph{compress} its model.
\end{enumerate}
%
All classifiers were trained for 20 iterations on one dataset before
being evaluated on the other.

@@

\paragraph{Results}
\autoref{fig:accuracy-results} shows the results of our experiment.
%
Localizing the type errors in our benchmarks amounted on average to
selecting one of 2--3 correct locations out of a slice of 10--11.
%
Our baseline of selecting at random is able to achieve 30\% Top 1
accuracy (58\% Top 3), while \ocaml achieves a Top 1 accuracy of 45\%.
%
Interestingly, one only needs two \emph{random} guesses to outperform
\ocaml, with 47\% accuracy.
%
\sherrloc outperforms both baselines with 56\% Top 1 accuracy (84\% Top
3), while \mycroft actually underperforms \ocaml with 38--41\% Top 1
accuracy.
%
Finally, we find that \emph{all} of our classifiers outperform \sherrloc,
ranging from 60--62\% Top 1 accuracy (85--88\% Top 3) for the \linear
classifier to 71--73\% Top 1 accuracy (91\% Top 3) for the \hiddenFH.

Interestingly there is little variation in accuracy between classifiers
with the exception of the \linear model, they all achieve around 70\%
Top 1 accuracy and around 90\% Top 3 accuracy.
%
In particular, the \hiddenT only loses around 2\% accuracy compared to
the \hiddenFH, which suggests that it can substantially compress the
model.
%
We also note that our classifiers consistently perform better when
trained on the \FALL programs and tested on the \SPRING programs than
vice versa, they appear to generalize better from the \FALL data.

### 2017-03-24 paper/oopsla17-submission/evaluation-utility.tex
more eval

\subsection{Feature Utility}
\label{sec:feature-utility}

\subsubsection{Type Error Slice}
\label{sec:type-error-slice}
The \InSlice feature should be highly predictive --- a fix must change
at least one expression in the type-error slice.
%
Thus, our first experiment seeks to quantify the impact of \InSlice by
comparing the accuracy of a linear model on three sets of features.
%
\begin{enumerate}
\item A baseline with only local syntactic features.
\item extends (1) with \InSlice.
\item discards samples from (1) where \InSlice is \emph{disabled}.
\end{enumerate}
%
The key difference between (2) and (3) is that a model for (2) must
\emph{learn} that \InSlice is a strong predictor.
%
In contrast, a model for (3) must only learn about the syntactic
features, the decision to discard samples where \InSlice is disabled has
already been made by a human.
%
This has a few additional advantages: it reduces the search space by a
factor of 7 on average, and it guarantees that any prediction made by
the classifier can fix the type error.
%
We expect that (2) will perform better than (1) as it has more
information, and that (3) will perform better than (2) as it does not
have to learn the importance of \InSlice.

@@

\begin{table}[ht]
  \begin{minipage}{0.49\linewidth}
  \centering
  \linear
  \begin{tabular}{lrrrr}
    \toprule
    Feature Set  & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax & 23.6\% & 42.6\% & 56.3\% & 19.6\% \\
    With Slice   & 46.4\% & 65.0\% & 75.4\% & 30.4\% \\
    Only Slice   & 54.9\% & 71.4\% & 82.5\% & 57.6\% \\
    \bottomrule
  \end{tabular}
  \end{minipage}
  \begin{minipage}{0.49\linewidth}
  \centering
  \hiddenF
  \begin{tabular}{lrrrr}
    \toprule
    Feature Set  & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax & 30.9\% & 47.9\% & 58.6\% & 20.6\% \\
    With Slice   & 54.5\% & 70.5\% & 81.5\% & 34.7\% \\
    Only Slice   & 56.7\% & 72.3\% & 82.9\% & 58.0\% \\
    \bottomrule
  \end{tabular}
  \end{minipage}
  \caption{
    Impact of type-error slice on accuracy.
    \ES{TODO: expand caption}
    \ES{TODO: load these numbers from CSV}
  }\label{tab:type-error-slice}
\end{table}

@@

\begin{table}[ht]
  \begin{minipage}{0.49\linewidth}
  \centering
  \linear
  \begin{tabular}{lrrrr}
    \toprule
    Feature Set                 & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax                & 55.0\% & 71.6\% & 82.6\% & 57.7\% \\
    \midrule
    + Size                      & 55.8\% & 72.8\% & 82.5\% & 57.3\% \\
    + Context                   & 59.9\% & 77.7\% & 86.4\% & 63.0\% \\
    + Types                     & 62.2\% & 77.7\% & 85.7\% & 62.2\% \\
    \midrule
    + Size + Context            & 60.2\% & 77.9\% & 86.0\% & 62.5\% \\
    + Size + Types              & 62.0\% & 78.2\% & 85.6\% & 62.3\% \\
    + Context + Types           & 63.2\% & 80.3\% & 87.9\% & 65.4\% \\
    \midrule
    + All                       & 62.3\% & 80.0\% & 88.0\% & 65.4\% \\
    \bottomrule
  \end{tabular}
  \end{minipage}
  % \begin{minipage}{0.49\linewidth}
  % \centering
  % \hiddenF
  % \begin{tabular}{lrrrr}
  %   \toprule
  %   Feature Set                 & Top-1  & Top-2  & Top-3  & Recall \\
  %   \midrule
  %   Local Syntax                & 56.9\% & 72.2\% & 82.8\% & 57.9\% \\
  %   \midrule
  %   + Size                      & 59.7\% & 74.6\% & 83.0\% & 57.4\% \\
  %   + Context                   & 70.9\% & 83.7\% & 90.4\% & 69.2\% \\
  %   + Types                     & 72.1\% & 84.1\% & 90.3\% & 69.3\% \\
  %   \midrule
  %   + Size + Context            & 69.8\% & 83.5\% & 90.2\% & 68.6\% \\
  %   + Size + Types              & 72.3\% & 84.6\% & 90.3\% & 69.5\% \\
  %   + Context + Types           & 75.5\% & 86.4\% & 91.5\% & 71.7\% \\
  %   \midrule
  %   + All                       & 75.0\% & 86.8\% & 91.9\% & 72.0\% \\
  %   \bottomrule
  % \end{tabular}
  % \end{minipage}
  % \\
  \begin{minipage}{0.49\linewidth}
  \centering
  \hiddenFH
  \begin{tabular}{lrrrr}
    \toprule
    Feature Set                 & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax                & 56.3\% & 72.1\% & 82.8\% & 57.6\% \\
    \midrule
    + Size                      & 60.5\% & 75.0\% & 83.8\% & 57.9\% \\
    + Context                   & 71.4\% & 84.1\% & 90.8\% & 69.5\% \\
    + Types                     & 73.2\% & 84.8\% & 90.2\% & 69.2\% \\
    \midrule
    + Size + Context            & 71.7\% & 83.5\% & 90.7\% & 69.3\% \\
    + Size + Types              & 73.5\% & 85.8\% & 91.4\% & 70.5\% \\
    + Context + Types           & 77.3\% & 87.5\% & 92.4\% & 72.9\% \\
    \midrule
    + All                       & 77.2\% & 87.9\% & 92.7\% & 72.9\% \\
    \bottomrule
  \end{tabular}
  \end{minipage}
  \caption{
    Impact of contextual features on accuracy.
    \ES{TODO: expand caption}
    \ES{TODO: load these numbers from CSV}
  }\label{tab:type-error-slice}
\end{table}

>>>>

\subsection{Feature Utility}
\label{sec:feature-utility}
We have shown that we can train a classifier to effectively localize
type errors, but which of the 276 features that we use are contributing
the most?
%
In order to answer this question we investigate the performance of
classifiers trained on various subsets of the features.

\subsubsection{Type Error Slice}
\label{sec:type-error-slice}
The \InSlice feature should be highly predictive --- a fix must change
at least one expression in the type-error slice.
%
Thus, our first experiment seeks to quantify the impact of \InSlice by
comparing the accuracy of a linear model on three sets of features:
%
\begin{enumerate}
\item A baseline with only local syntactic features.
\item The local syntactic features of (1) extended with \InSlice.
\item The same features as (1), but we preemptively discard samples
  where \InSlice is \emph{disabled}.
\end{enumerate}
%
The key difference between (2) and (3) is that a classifier for (2) must
\emph{learn} that \InSlice is a strong predictor.
%
In contrast, a classifier for (3) must only learn about the syntactic
features, the decision to discard samples where \InSlice is disabled has
already been made by a human.
%
This has a few additional advantages: it reduces the set of candidate
locations by a factor of 7 on average, and it guarantees that any
prediction made by the classifier can fix the type error.
%
We expect that (2) will perform better than (1) as it contains more
information, and that (3) will perform better than (2) as the classifier
does not have to learn the importance of \InSlice.

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{lrcrrrrcrrrr}
    \toprule
                 &             & & \multicolumn{4}{c} \linear        & & \multicolumn{4}{c} \hiddenF       \\
                                   \cmidrule{4-7}                        \cmidrule{9-12}
    Feature Set  & \# Features & & Top-1  & Top-2  & Top-3  & Recall & & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax & 47          & & 23.6\% & 42.6\% & 56.3\% & 19.6\% & & 30.9\% & 47.9\% & 58.6\% & 20.6\% \\
    + Slice      & 48          & & 46.4\% & 65.0\% & 75.4\% & 30.4\% & & 54.5\% & 70.5\% & 81.5\% & 34.7\% \\
    Only Slice   & 47          & & 54.9\% & 71.4\% & 82.5\% & 57.6\% & & 56.7\% & 72.3\% & 82.9\% & 58.0\% \\
    \bottomrule
  \end{tabular}
  \caption{
    Impact of type-error slice on accuracy.
    \ES{TODO: expand caption}
    \ES{TODO: load these numbers from CSV}
  }\label{tab:type-error-slice}
\end{table}

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{lrcrrrrcrrrr}
    \toprule
                             &             & & \multicolumn{4}{c} \linear        & & \multicolumn{4}{c} \hiddenFH      \\
                                               \cmidrule{4-7}                        \cmidrule{9-12}
    Feature Set              & \# Features & & Top-1  & Top-2  & Top-3  & Recall & & Top-1  & Top-2  & Top-3  & Recall \\
    \midrule
    Local Syntax             &  44         & & 55.0\% & 71.6\% & 82.6\% & 57.7\% & & 56.3\% & 72.1\% & 82.8\% & 57.6\% \\
    \midrule
    + Size                   &  45         & & 55.8\% & 72.8\% & 82.5\% & 57.3\% & & 60.5\% & 75.0\% & 83.8\% & 57.9\% \\
    + Context                & 220         & & 59.9\% & 77.7\% & 86.4\% & 63.0\% & & 71.4\% & 84.1\% & 90.8\% & 69.5\% \\
    + Types                  & 102         & & 62.2\% & 77.7\% & 85.7\% & 62.2\% & & 73.2\% & 84.8\% & 90.2\% & 69.2\% \\
    \midrule
    + Context + Size         & 221         & & 60.2\% & 77.9\% & 86.0\% & 62.5\% & & 71.7\% & 83.5\% & 90.7\% & 69.3\% \\
    + Types + Size           & 103         & & 62.0\% & 78.2\% & 85.6\% & 62.3\% & & 73.5\% & 85.8\% & 91.4\% & 70.5\% \\
    + Context + Types        & 275         & & 63.2\% & 80.3\% & 87.9\% & 65.4\% & & 77.3\% & 87.5\% & 92.4\% & 72.9\% \\
    \midrule
    + Context + Types + Size & 276         & & 62.3\% & 80.0\% & 88.0\% & 65.4\% & & 77.2\% & 87.9\% & 92.7\% & 72.9\% \\
    \bottomrule
  \end{tabular}
  % \begin{minipage}{0.49\linewidth}
  % \centering
  % \hiddenF
  % \begin{tabular}{lrrrr}
  %   \toprule
  %   Feature Set                 & Top-1  & Top-2  & Top-3  & Recall \\
  %   \midrule
  %   Local Syntax                & 56.9\% & 72.2\% & 82.8\% & 57.9\% \\
  %   \midrule
  %   + Size                      & 59.7\% & 74.6\% & 83.0\% & 57.4\% \\
  %   + Context                   & 70.9\% & 83.7\% & 90.4\% & 69.2\% \\
  %   + Types                     & 72.1\% & 84.1\% & 90.3\% & 69.3\% \\
  %   \midrule
  %   + Size + Context            & 69.8\% & 83.5\% & 90.2\% & 68.6\% \\
  %   + Size + Types              & 72.3\% & 84.6\% & 90.3\% & 69.5\% \\
  %   + Context + Types           & 75.5\% & 86.4\% & 91.5\% & 71.7\% \\
  %   \midrule
  %   + All                       & 75.0\% & 86.8\% & 91.9\% & 72.0\% \\
  %   \bottomrule
  % \end{tabular}
  % \end{minipage}
  % \\
  % \begin{minipage}{0.49\linewidth}
  % \centering
  % \hiddenFH
  % \begin{tabular}{lrrrr}
  %   \toprule
  %   Feature Set                 \\
  %   \midrule
  %   Local Syntax                \\
  %   \midrule
  %   + Size                      \\
  %   + Context                   \\
  %   + Types                     \\
  %   \midrule
  %   + Size + Context            \\
  %   + Size + Types              \\
  %   + Context + Types           \\
  %   \midrule
  %   + All                       \\
  %   \bottomrule
  % \end{tabular}
  % \end{minipage}
  \caption{
    Impact of contextual features on accuracy.
    \ES{TODO: expand caption}
    \ES{TODO: load these numbers from CSV}
  }\label{tab:type-error-slice}
\end{table}

### 2017-03-24 paper/oopsla17-submission/evaluation.tex
more eval

\subsection{Experimental Setup}
\label{sec:experimental-setup}

@@

>>>>

\subsection{Methodology}
\label{sec:methodology}

@@

\paragraph{Accuracy Metric}
All of the tools we compare (with the exception of \ocaml) can produce a
list of potential error locations, which might in the limit include the
entire type error slice.
%
However, in a study of fault localization techniques,
\citet{Kochhar2016-oc} show that most developers will not consider more
than around five potential error locations before falling back to manual
debugging.
%
Type errors are relatively simple in comparison to general fault
localization, thus we limit our evaluation to the top three predictions
of each tool.
%
We evaluate each tool on whether a changed expression occurred in its
top 1, top 2, or top 3 predictions.
